{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-11-20 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

        Using convexity, it transform the inequality into 

@@

        The second last inequality use the fact that $(1 - \alpha_k)/\alpha_k^2 = \alpha_{k - 1}^{-2}$ and $\alpha_1 = 1$. 

@@

        Therefore 

@@

            One may use KL-Convergence framworks to strengthens the convergence claim of the Catalyst by establishing convergence to a limiting stationary point. 

>>>>

        Using convexity, it transforms the inequality into 

@@

        The second last inequality uses the fact that $(1 - \alpha_k)/\alpha_k^2 = \alpha_{k - 1}^{-2}$ and $\alpha_1 = 1$. 

@@

        Therefore, 

@@

            One may use KL-Convergence frameworks to strengthen the convergence claim of the Catalyst by establishing convergence to a limiting stationary point. 
